---
title: "Hurricane Andrew"
author: "Lauren, Kayla, Andrew"
date: "11/20/2021"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#source(file = "Andrew_Data_Source.R")
source(file = "Variogram Source.R")
library(shiny)
```

## Overview of Hurricane Andrew 1992

- Devastating Category 5 hurricane (3rd strongest US hurricane)  
- Recorded Landfall:     
  - August 24th : Florida  
  - August 26th : Louisiana  
- Total 65 dead and $27.3 billion in damage  


## Hurricane Path

```{r, echo = FALSE}
andrew_buoy_map
```

## Interactive Map 

```{r}
ui_1 <- fluidPage(
  selectInput("Day", "select day", unique(all_buoy$Day)), 
  plotOutput("plot", brush = "plot_brush"),
  tableOutput("data")
)
server_1 <- function(input, output, session) {
    output$plot <- renderPlot({
    plot_data_buoy <- all_buoy %>% subset(Day == input$Day)
      base_map + 
        geom_path(data = andrew, aes(x = longitude, y = latitude), color = "blue", size = 1) + 
        geom_point(data = plot_data_buoy, aes(x = longitude, y = latitude))
    }, res = 96, height = 400, width = 600)
    
    output$data <- renderTable({
    brushedPoints(subset(all_buoy, Day == input$Day), input$plot_brush)
  })
      
}

shinyApp(ui_1, server_1)
```

## Variogram Windspeed

```{r, fig.height= 4}
plot(vario_wspd, fit1)
```

- <font size = "4"> no clear apparent sill </font> 
- <font size = "4"> spacial autocorrelation appears to be present throughout all distances  </font>
  - <font size = "4"> could suggest that a trend is present in the data </font>

## Variogram Windgusts

```{r, fig.height= 4}
plot(vario_gst, fit2)
```

- <font size = "4"> quickly reaches its apparent sill well before distance reaches a value of 1 </font>  
  - <font size = "4"> suggests spacial autocorrelation is not present beyond the range </font>

## Variogram Barometric Pressure

```{r, fig.height= 4}
plot(vario_bar, fit3)
```

- <font size = "4"> reaches its apparent sill at about a distance of 4 </font>
  - <font size = "4"> suggests that spacial autocorrelation is no longer present beyond the range </font>
